Autonomous Realization of Simple Machines

### 2014-05-23 doc/paper/paper.tex
..

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}

@@

\title{Autonomous Realization of Simple Machines}
\author{Can Erdogan \and Mike Stilman}
\institute{Institute for Robotics and Intelligent Machines \\Georgia Institute of Technology}

\maketitle

@@

\section{Technical Approach}

We now present our approach to autonomous construction of simple machines, particularly a
lever-fulcrum assembly to overturn heavy obstacles, in four major categories: (1) autonomous design,
(2) visual perception, (3) posture control, and (4) motion planning.

In any design, components have to be placed to satisfy a set of physical or domain constraints. For
instance, a candidate 2-by-4 block needs to make contact both with the load and the fulcrum,
essentially distance functions between objects, to satisfy physical constraints of the design.
However, for a design to be useful, we also impose that the contact point for the lever is further
away from the fulcrum than the load such that a mechanical advantage is achieved. In previous work,
we propose a nonlinear optimization approach where such geometric and dynamic constraints are
expressed as equality and inequality functions whose common zero-crossings are design configurations
that satisfy all the constraints. For this work, we use the planner to output the lever and the
fulcrum configurations, and the required contact point, but allow the robot to choose its closest
configuration, assuming it can supply the necessary force.

In perceiving the environment, we propose using a light-weight feature-based recognition approach as
opposed to full 3D based approaches that use the entire mesh data such as the iterative closest
point algorithm or over-segmentation methods. The key assumption of the work is that the planner
already knows the mesh of the available objects and with minimal additional feature knowledge, such
as the top of a cinder block is at 44 cm from the ground or a lever is at least 2 meters in one
dimension, we can speed up detection. At its current stage, the agent can autonomously detect cinder
blocks, the load as shown in Figure 1, the walls and the 2-by-4 levers. To localize objects of
interest, we perform a simple scan with the tilt and pan degrees of freedom of the RGBD camera,
taking also into account the robot kinematics. Figure \ref{fig:detection} demonstrates the detection module.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=1.0\linewidth]{Figures/detection.png}
  \caption{The mechanical advantage in forces}
  \label{fig:detection}
\end{figure}

For the locomotion controllers, we model Krang as a simple inverse pendulum and use a
proportional-derivative control with gain scheduling for different robot poses to minimize the
frequency of oscillations in dynamic balancing. In picking up cinder blocks, the torque around the
wheel axis due to the additional force at the end-effector is incorporated in computing the goal
balancing angle.

Lastly, for motion planning, we use a variety of approaches. First, to grasp objects, we use
analytical inverse kinematics to determine if there is a configuration close to the object we can
reach without collisions. Once close, we perform Jacobian inverse kinematics to approach the object
and detect contact with the object with the gripper force-torque sensor. Analytical inverse
kinematics is used as a resolution-complete method to determine whether a collision-free grasp
configuration exists as opposed to sampling the large configuration space of the arms to avoid local
minima with Jacobians. In addition to motion planning for the arms, we also make use of an example
of conformant planning in picking up a lever. The motivation is to avoid perception problems by
running each wheel to the 2-by-4 on the ground while the wheels cannot exert the torque to climb
over the object. Thus, the robot autonomously aligns itself with the object of interest by using
contact points without the need for precise perception.

\section{Results}

Our results demonstrate Golem Krang autonomously construct a simple machine design, specifically a
lever-fulcrum assembly, and use it to overturn a 45 kg load. To achieve such an autonomous behavior,
we propose a set of modules that accomplish object detection and localization, balancing and
navigation controller in the presence of external disturbances, and a rich set of motion planning
modules. To demonstrate the execution of the task, we designed the following scenario (see
\url{http://tinyurl.com/mw2ehxl} for video):

We position Golem Krang in the middle of the room and instruct it to use the closest cinder block as
a fulcrum. Using the aforementioned tools, the robot picks up the object (e.g. reacts to its weight
by leaning backwards) and carries it to the predetermined position instructed by the constraint
optimization planner. During locomotion, we assume that there are no obstacles on the path of the
robot, and the robot uses the turn-forward-turn tactic to move between two planar poses. Once the
robot places the fulcrum, it scans its surroundings for a lever and once located, approaches it
using the perception data. To minimize the effect of perception errors, once within 0.5 meters of
the lever, the robot deploys the wheel contact approach to position itself exactly in front of the
object and takes it back to the load. Finally, the robot positions the lever with Jacobian control
and exerts force with the top joint in its 7-dof arm.

\section{Experiments}

A significant challenge in accomplishing the series of the autonomous manipulation and perception
tasks has been the accumulation of error over the course of the executions. To remedy such an error
build-up, at the current state of our work, the authors intervene and instruct the robot to minimize
its position errors. We focus on the two main reasons and propose possible solutions.

During experiments, we observed that the RGBD data becomes more erroneous as the distance increases.
Within a 1 meter bound, the mean error is within 2-3 cm whereas with the maximum 4 meters (e.g. the
room limits), we see errors up to 10 cm. The proportional increase of error with respect to distance
suggest a camera calibration problem. Another source of error could be the slack in the tilt and pan
joints that control the camera view. The general of camera calibration has been addressed via bundle
adjustment in [2].

A second reason we suspect that might lead to localization errors is the error accumulated while the
robot attempts to follow a velocity profile in the forward direction. Figure \ref{fig:controller} demonstrates the
reference position and velocity trajectories (green), along with the real trajectories (red). To
remedy this error, we will focus on the trajectory following techniques developed by [7].

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/controller.png}
  \caption{The mechanical advantage in forces}
  \label{fig:controller}
\end{figure}

Lastly, the main experiment of our work is the successful overturning of the 45 kg obstacle. Figure
4 demonstrate the forces measured at the robot gripper as it pushes the lever until the obstacle
falls. Given that the load is approximately 500N and the maximum force is 250N, we observe an
advantage of 2:1.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.6\linewidth]{Figures/plot.png}
  \caption{The mechanical advantage in forces}
  \label{fig:plot}
\end{figure}

\section{Experimental Insights}

We offer two insights from our experiments. First, the manipulation of heavy objects brings about
interesting challenges. If the object inertia model is not known, the system can be thrown off
balance easily. Moreover, when the mass of the object is mostly on one of the wheels, the robot can
start spinning since one wheel has to accommodate the extra weight. Second, the constraint
optimization planner outputs too precise (e.g. 1$e^{-5}$) configurations which we observe clearly
cannot be executed to the same level of precision. We propose extending the planner for iterative
solutions and/or soft constraints.

\bibliographystyle{plain}
\bibliography{references}

@@

>>>>

\documentclass[runningheads,a4paper]{llncs}
% \documentclass{article}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage[algoruled, vlined,linesnumbered]{algorithm2e}

@@

\title{Autonomous Realization of Simple Machines}
\author{Can Erdogan \and Mike Stilman}
\institute{Institute for Robotics and Intelligent Machines \\Georgia Institute of Technology}
\maketitle

@@

\newpage
\section{Technical Approach}

\subsection{Constraint Satisfaction for Simple Machine Designs}

The manipulation of multiple objects to achieve a goal can be readily represented in a constraint
satisfaction paradigm where the constraints represent the relationships between the design
components. In this work, we focus on simple machine designs such as lever-fulcrum assemblies or
inclined planes that need to be structurally stable and provide mechanical leverage to their users.
Reasoning about such design criteria requires analysis of more detailed concepts such as center
of masses, robot kinodynamic constraints and physics principles.

The process for an autonomous planner is composed of three steps. First, from the set of available objects
in the environment, it needs to choose a subset that will be incorporated in the structure. Second,
the structure components are assigned roles that designate how they should be put together - specifically,
the constraints that \textit{bind} one to another. Lastly, the planner needs to configure the objects
such that the role constraints and the general design criteria are satisfied.

\subsubsection{Component Choices}

A completeness property for an autonomous planner for structural designs is a crucial advantage
for deployment in real-world circumstances (e.g. military or search-and-rescue operations). In
emergency situations, when physically challenging that requires creative reasoning about simple
machines usually arise, the ability to exhaustively search for all possible solutions and determine
if one exists is a critical advantage. Note that we assume every object is used only once in the 
structure as opposed to the agent changing the structure as its being used.

In choosing a set of design components, an autonomous planner needs to exhaustively search the 
entire \textit{finite} space of discrete assignments. In comparison to continuous choices, such as
object configurations, the discrete nature of the choices (i.e. in or out) makes such a search
feasible. Despite the finite space, it is challenging to evaluate
every alternative since there is still a combinational number of roles and infinite 
space of configurations to reason about.

To remedy the computational challenge, pruning strategies and heuristics are significant tools in
cutting back the search at the top level. For instance, in construction a lever-fulcrum design,
two wooden blocks of the same size (or approximately to a degree of confidence) can be categorized
under one class. Similarly, for loads that are known to be significantly heavier than a robot can
handle, the longer lever candidates might be priotized in the search process.

\subsubsection{Object Roles}

Imagine a two-step stairs is needed to enable a swarm of rough-terrain vehicles, such as 
PackBots or RHexs \cite{yamauchi2004packbot,saranli2001rhex}, climb a window and survey a building, and some of them have robotic
arms that can stack box-like objects. The goal for a planner would be to choose three boxes and
stack two of them (e.g. box B on C) such that the swarm can first climb one step and then move on to
the two stack, until it reaches the window sill.

In coming up with this solution, two types of choices need to made. First, among the three objects,
say A, B, and C, which object would constitute as the first step and which one would be at the top
in the second step needs to be decided. Secondly, to place the objects on the ground or on top of
another object, a base face needs to be chosen to clarify the object roles and to simplify the
representation of the constraints for the object configurations. Note that choosing a base 
in fact partitions the configuration space of the objects even before the design constraints
are considered to prune infeasible assignments.

The goal of the object roles is to specify (1) the relationship of a component with respect to
others, and (2) which of its face and edges are used in these connections. Figure \ref{fig:matches} 
\cite{erdogan2014incorporating} demonstrates some outcome assemblies with the triangle prism
object acting as fulcrum positioned on different base faces and in contact with the chosen lever
on various edges. Similarly, we observe that the lever can be used on at least two of its faces
(discounting symmetries) while it is still possible to find a feasible assembly.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.7\linewidth]{Figures/matches.png}
  \caption{Different face and edge assignments for the lever-fulcrum assembly. Some assignments,
  such as using the shortest edge of the lever to connect the fulcrum and the load, may not
  be feasible due to design constraints and collisions.}
  \label{fig:matches}
\end{figure}

The role assignment to available resources has been a thoroughly studied area, starting from
classical planning \cite{newell1961gps,mccarthy1963programs}, and evolving into operations research
\cite{fulkerson1961network,taha1975integer}, and in this work, we adopt the STRIPS representation
for the planning process \cite{fikes1972strips}. The idea is to provide the domain knowledge of possible
actions to take on the available objects in the environment. For instance, a lever can be \textit{placed}
on a fulcrum or a ramp can be \textit{rested} against another object. A minor difference in our
framework is that every action induces additional constraints to the assembly configurations and
an action can be taken if and only if there exists some configuration that satisfies the accumulated
constraints.

\subsubsection{Continuous Configuration Space and Constraints}

The proposed framework accumulates design constraints via a classical planning framework
and a feasibility process determines whether the constraints can be satisfied by some configuration
of the components. The idea is that the different type of constraints can all be generically
expressed as equality or inequality functions on the space of object and robot configurations.
If all the constraints are convex, for instance in a stair or bridge design with simplified
robot assumptions, the feasibility can be determined by an efficient simplex algorithm
implementation \cite{erdogan2013planning}. For the larger set of nonconvex domains, especially when
robot kinodynamics are considered, we propose a nonlinear optimization process which minimizes the
violation of the constraints and attempts to find an assignment of configurations that satisfies all of them.

A number of design constraints such as stacking a box on top of another one or placing a lever
at the edge of a fulcrum can be expressed with geometric projections. Figure \ref{fig:constraints}
demonstrates three types of connections: (1) center of mass-face, (2) edge-face, and (3) face-face. 
The general idea is that points of interest such as center of mass, endpoints of an edge or vertices
of a face are projected to the plane of another face and limits are imposed on its location. For instance,
for two objects to be stacked successfully (A), the center of mass of the top object has to lie within
the supporting face of the bottom object. Similarly, to ensure an edge is on a face (B), it is sufficient
to confine the endpoints of the edge onto the face plane and guarantee there exists a shared point
(e.g. cross) between the edge and the face. Lastly, for contact between two faces (C), 
three points of one of the faces has to lie on the other one and again, a shared point should exist.
Observe that geometric contact concepts are easily expressed through equality
and inequality expressions on the projections of significant points on the meshes.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.75\linewidth]{Figures/constraints.png}
  \caption{Visualization of different types of geometric contact constraints}
  \label{fig:constraints}
\end{figure}

Once the object choices and roles are determined, the equality and the inequality constraints between
the assembly components can be gathered into two sets $\mathcal{F}$ and $\mathcal{G}$ respectively.
The idea behind using optimization to find feasible samples in the configuration space is based on
creating error functions by the violation of the constraints for a sample $\vec{x}$:

\vspace{-1em}
\begin{align*}
f(\vec{x}) = 0 \;\; \Rightarrow & \;\; E_f(\vec{x}) = f^2(\vec{x}) \\
g(\vec{x}) \leq 0 \;\; \Rightarrow & \;\; E_g(\vec{x}) = 
	\begin{cases}
		g^2(\vec{x}) & \text{if $g(\vec{x}) > 0 $}, \\
	0        & \text{otherwise}.
	\end{cases}
\end{align*}

\noindent where $E_f(\vec{x})$ and $E_g(\vec{x})$ are the proposed squared error functions. Now,
given the constraint sets $\mathcal{F}$ and $\mathcal{G}$, we define the total error:

\begin{equation}
	\mathcal{E}(\vec{x}) = \sum\limits_{f \in \mathcal{F}} E_f(\vec{x}) + \sum\limits_{g \in \mathcal{G}} E_g(\vec{x}).
\end{equation}

\noindent Note that $\mathcal{E}(\vec{x})$ is 0 for
some $\vec{x}$ if and only if configurations $\vec{x}$ satisfy all the design
constraints. Moreover, the global minima is guaranteed be more than or equal
to 0 since the function is a sum of squared errors. Then, by using an optimization method, such as
Levenberg-Marquardt, the global minima could be found through sampling the space for good initializations.

We outline the overall approach in Algorithm 1 below. Given the available objects, the goal
criteria and the available actions, the planner searches in the space of discrete object roles
(line 3) and attempts to take actions as long as they lead to feasible configurations (line 9). The forward
search accumulates constraints until a feasible design is reached or backtracks.

\begin{algorithm}[ht!]
  \SetCommentSty{emph}
  \KwIn{$domain$: objects properties and generic actions; $goals$: list of goal literals to be fulfilled; $initialState$: discrete literals and no constraints; }
  \KwResult{configurations: a feasible value in goal subspace; }
  $stateStack \leftarrow $createStack$(initialState);$ \\
  \While{$state \leftarrow stateStack$.pop$()$} {
    $actions \leftarrow $stateActions$(domain)$; \\
    \ForEach{$action$ in the set $actions$} {
      \If{$action.pres \subset state.literals$} {
				newConsts $\leftarrow$ state.consts $\cup$ action.consts; \\
				\For{$counter = 1 \dots MAX\_COUNT$} {
					\{\textit{localMin, confs}\} $\leftarrow $optimize($newConsts$, newSeed($domain$)); \\
					\If{abs$(localMin) \leq 1e^{-4}$} {
						\lIf{$goals \subset action.afters$} \Return{confs}; \\
						\Else{
							$child = \{state.literals \cup action.afters, newConsts\}$ \\
							$stateStack$.push($child$); \\
							\textbf{break}; \\
						}
					}
				}
			}
		}
  }
  \Return{$\emptyset$}; 
  \caption{ConstraintPlanner()}
\end{algorithm}

\subsection{Humanoid Robot Platform: Golem Krang}

Designed and built in the Humanoid Robotics Laboratory, Golem Krang is a 150 kg, 6.2 m segway-like
humanoid robot with two wheels that uses a balancing strategy for locomotion and manipulation \cite{stilman2010golem}.
Given its unique design, an autonomous planner for functional structures needs to address several
hardware constraints. First, the contact point on the lever needs to be reachable by the robot.
Second, the robot needs to apply sufficient force to overcome the opposing weight or friction. For
Golem Krang, we opt to use only the waist and the wheel motors (Figure 1), and choose to fix the
arms with hard mechanical breaks. The motivation is three-fold: (1) the chosen joints have
sufficient torque to actuate the simple machine, (2) simpler reasoning about reachable space of the
end-effectors, and (3) hardware safety in manipulating hundreds of kgs of objects with an already
heavy robot. Lastly, Golem Krang needs to maintain a stable posture before contact is made with the
structure.

\subsection{Perception}

Equipped with a two degree of freedom platform that houses a Microsoft Kinect, Golem Krang can
inspect and reason about its environment with visual data. In perceiving the environment, we propose
using a light-weight feasure-based recognition approach as opposed to full 3D based approaches that
use the entire mesh data such as the iterative closest point algorithm or over-segmentation methods.
Figure \ref{fig:detection} demonstrates a sample output of the framework.

\begin{figure}[ht!] 
  \centering
  \includegraphics[width=0.9\linewidth]{Figures/detection.png}
  \caption{Cinder block and wooden plates detected as fulcrum and lever objects.}
  \label{fig:detection}
\end{figure}

The key assumption of the work is that the planner already knows the mesh of the available objects
and with minimal additional feature knowledge, such as the top of a cinder block is at 44 cm from
the ground or a lever is at least 2 meters in one dimension, we can speed up the detection. At its
current stage, the agent can autonomously detect cinder blocks, the load as shown in Figure 1, the
walls and the 2-by-4 levers. To localize objects of interest, we perform a simple scan with the tilt
and pan degrees of freedom of the RGBD camera, taking also into account the robot kinematics.

\subsection{Locomotion}

% Why balance?
% How to balance? 
% How to balance while carrying objects?

\newpage
\bibliographystyle{plain}
\bibliography{references}

@@

% DISCUSSION: CHALLENGES WITH VISUAL SERVOING A NONHOLONOMIC ROBOT BASE

% Having chosen the objects and their roles, the autonomous planner needs to find configurations
% for the assembly components to satisfy a range of constraints. First, the proposed assembly needs
% to be physically stable (e.g. all center of masses of upper layers within support polygons) and 
% collision-free. Second, the structure should satisfy its purpose, such as overturning a load,
% while taking into account the actuator robot's kinodynamic limitations, possibly guided by design
% principles such as the input arm of a lever being longer than the load arm for mechanical advantage.
% Note that in considering the robot limitations, we focus on the initial moment of actuation where
% presumably the required force input is maximal and output a robot configuration and required joint
% torques along with the design that is sufficient to realize the task.
